Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-17 paper/paper.tex
adding plot and massaging text

The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity, which is specially rich in this
domain. We report results in three parts. First, we report on the
stability of the engines we analyzed using the Test262 standard
conformance test suite for EcmaScript~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). The intuition is that the bugs we
discover throughout this study would have low relevance if the engines
are too fragile. Second, we report results obtained with test
transplantation (Section~\ref{sec:transplantation}). The rationale is
that the domain of possible inputs is too large; consequently, we
expect that test suites written for a given engine cover scenarios and
corner cases uncovered by another engine. To sum, we conjecture that
test cases written for one engine could reveal bugs in different
engines as opposed to only manifesting false alarms. Third, we
analyzed the impact of using cross-engine differential testing to find
bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
rationale is that even black-box fuzzers that typically make valid
changes only in literals of the language could expose important
bugs. All in all, we want to assess the impact of practical approaches
that leverage diversity to find bugs in \js\ engines.

\subsection{Stability of Engines}
\label{sec:stability}

We evaluated stability with Test262~\cite{ecma262-conformance-suite},
the official \js{} conformance test suite for the ECMA262
specification. We ran this suite once a day for seven consecutive
days. Table~\ref{tab:test262} shows the number of failures over this
period. It is important to note that failures are expected as it takes
time for engines to adjust to the spec. It is also important to
highlight that all engines we analyzed, but \chakra{}, use some
variant of the Test262 suite as part of their regression
process\Mar{with fewer tests?}. We used the official version
instead\Mar{, which updates tests regularly?}. To sum, we observed
that \Fix{...} \Mar{justify regressions using the Kangax report}

@@

\subsection{Test Transplantation}
\label{sec:transplantation}

@@

\subsubsection{Results}
\Mar{revise text...}
\Fix{
Table~\ref{tab:summary-of-results} summarizes our results. It shows,
for each fuzzer and kind of bucket (\ie{}, hi or lo), the total number
of files involved, the number of buckets reported by our
infrastructure, the number of those that we classified as
bug-revealing (positive), and the number of those that we filed a bug
report. The difference between the last two columns corresponds to the
number of duplicates, \ie{}, the cases of bugs already reported in the
corresponding issue tracker. As expected, the hit ratio for the ``hi''
group is higher, indicating that chances of filing a bug report for a
``hi'' warning is higher.}

@@

@@

% \Igor{
%   Para realizar nossos experimentos, tivemos que decidir qual as 
%   melhores abordagens para aumentar a efetividade dos fuzzers.
%   Os fuzzers mutacionais se mostraram mais eficientes em relacao
%   aos fuzzers geracionais, entao focamos neste ponto.
%   Utilizamos os fuzzers radamsa, QuickFuzz e \Fix{others} nas suas configuracoes
%   default para realizar a mutacao em arquivos existentes.
%   O fuzzer radamsa eh um fuzzer mutacional agnostico de linguagem e possui algumas
%   deficiencias para a nossa infraestrutura como a falta de uma gramatica para guiar a suas mutacoes, 
%   pois muitas das vezes a unica mutacao ocorre em uma palavra dentro de um comentario por exemplo.
%   O fuzzer QuickFuzz tem uma gramatica JS integrada e sua mutacao ocorre de forma mais robusta que o 
%   radamsa, gerando arquivos mais relevantes.
%   Nossa infraestrutura usa a library Esprima\footnote{cite esprima url} para garantir que o arquivo fuzzado
%   é um arquivo de teste relevante, seguindo estes requisitos:
%   \begin{itemize}
%     \item it contains only unicode text
%     \item it is parseable (i.e., it is structurally well-formed)
%     \item it does not contain engine-specific functions  
%     \item it does not empty
%   \end{itemize}

% }

@@

%% Although there are many features yet to implement in our
%% infrastructure,

This section shows results obtained with our
infrastructure. Table~\ref{tab:bugs} shows the list of bugs we
reported on issue trackers of different engines in the period of 42
days. So far, ten of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that all bug
reports still waiting for confirmation are associated with the
\jsc{} engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. 
\Igor{
The bugs reported on \chakra{}'s bug tracker was defined as confirmed, 
however the bugs are included on a milestone for the next release
following an internal priority.
}
As of now, we did not find any new bug on \smonkey{} and V8; 
the bugs we found were duplicates and were not reported. Finally, it is
worth noting that \Fix{11 of the 19} JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from seven different open
source engines, including a total of 30K test files.

@@

\vspace{1ex}\noindent\textbf{Bug \# 6.} The JS code \CodeIn{var a = \{valueOf:~function()\{return
  ``\textbackslash{}x00''\}\} assert(+a === 0)\}} 
manifested a bug in the \js{} engine \chakra{}.  The object
property \CodeIn{valueOf} stores a function that returns a primitive
value identifying the target object~\cite{valueof}. The original
version of this code returns an empty string whereas the version of
the code modified by the Radamsa fuzzer~\cite{radamsa} returns a string
representation of a null character (called \CodeIn{NUL} in ascii). The
unary plus expression ``\CodeIn{+a}", appearing in the assertion, is
equivalent to the abstract operation \CodeIn{ToNumber(a.valueOf())}
that converts a string to a number, otherwise the operation returns
NaN (Not a Number)\cite{unary-plus}. For this case, \chakra{} evaluates
the unary plus to NaN as expected, as the null character cannot be
converted. As result, the test fails as expected. \chakra{}, in contrast,
incorrectly converts the string to zero, making the test to pass. All
other engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

>>>>

\Mar{REVISE}The goal of our study is to assess reliability of \js\ engines by
leveraging implementation diversity. We organized our study in three
parts. First, we report on the stability of the engines we analyzed
using the Test262 standard conformance test suite for
EcmaScript~\cite{ecma262-conformance-suite}
(Section~\ref{sec:stability}). The intuition is that the bugs we
discover throughout this study would have low relevance if the engines
are too fragile. Second, we report results obtained with test
transplantation (Section~\ref{sec:transplantation}). The rationale is
that the domain of possible inputs is too large; consequently, we
expect that test suites written for a given engine cover scenarios and
corner cases uncovered by another engine. To sum, we conjecture that
test cases written for one engine could reveal bugs in different
engines as opposed to only manifesting false alarms. Third, we
analyzed the impact of using cross-engine differential testing to find
bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
rationale is that even black-box fuzzers that typically make valid
changes only in literals of the language could expose important
bugs.

\subsection{Summary of Results}
\label{sec:summary}

Figure~\ref{fig:summary}...

\begin{figure}[h]
  \centering
  \includegraphics[trim=0 0 0 0,clip,width=0.4\textwidth]{R/stackedbar/stacked}  
  \caption{\label{fig:summary}Summary of results.}
\end{figure}

\subsection{Test Transplantation}
\label{sec:transplantation}
\label{sec:stability}

\Mar{REVISE}We evaluated stability with Test262~\cite{ecma262-conformance-suite},
the official \js{} conformance test suite for the ECMA262
specification. We ran this suite once a day for seven consecutive
days. Table~\ref{tab:test262} shows the number of failures over this
period. It is important to note that failures are expected as it takes
time for engines to adjust to the spec. It is also important to
highlight that all engines we analyzed, but \chakra{}, use some
variant of the Test262 suite as part of their regression
process\Mar{with fewer tests?}. We used the official version
instead\Mar{, which updates tests regularly?}. To sum, we observed
that \Fix{...} \Mar{justify regressions using the Kangax report}

@@

@@

\subsubsection{Results} Table~\ref{tab:summary-lo} shows statistics of \lo\ warnings obtained
when fuzzing inputs with different tools. Column ``\# buckets'' show
the number of buckets associated with ``\lo'' warnings whereas column
``avg. \# files per bucket'' show the average number of files per
bucket. Note that \Fix{...}

@@

Table~\ref{tab:summary-hi} shows the number of \hi\ warnings reported
per engine. Recall that we did not cluster \hi\ warnings as there was
not clear clustering criteria to use for that. Note that \Fix{...}

@@

Table~\ref{tab:bugs} shows the list of bugs we reported with
differential testing across five months of analysis. The table is
organized in two sections. The top section shows results obtained
during the exploratory phase of the study and the bottom section shows
the results obtained during the non-exploratory phase. The table shows
the date the bug was reported (``Date''), the fuzzing tool used to
detect the bug (``Fuzz''), the \js\ engine affected (``Engine''), the
status of the bug report as of Aug. 24, 2018 (``Status''), the Url of
the bug report (``Url''), the severity of the bug report
(``Severity''), the priority that we assigned to the warning that
revealed the bug (``Priority''), and the test suite from the original
test input (``Suite'').

\Mar{REVISE}So far, ten of the bugs we
reported were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine implementations.
Note from the table that all bug reports still waiting for
confirmation are associated with the \jsc{} engine (JSC). A closer
look at the JSC issue tracker showed that the triage process is very
slow for that engine.  \Igor{ The bugs reported on \chakra{}'s bug
  tracker was defined as confirmed, however the bugs are included on a
  milestone for the next release following an internal priority.  } As
of now, we did not find any new bug on \smonkey{} and V8; the bugs we
found were duplicates and were not reported. Finally, it is worth
noting that \Fix{11 of the 19} JS files that manifested discrepancies
were \emph{not} produced with fuzzing (column ``Fuzz''). These are
test files from suites of different engines. This observation
emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from seven different open
source engines, including a total of 30K test files.

@@

@@

\sloppy
\vspace{1ex}\noindent\textbf{Bug \# \Fix{6}.} The JS code \CodeIn{\{var a =
  \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}} manifested a bug in the \js{} engine \chakra{}.
The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the Radamsa fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}",
used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
  chakra did that it would be fine, no?} evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As
result, the test fails as expected. \chakra{}, in contrast,
incorrectly converts the string to zero, making the test to pass. All
other engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.
